From Education to Entrepreneurship

### 2014-12-06 index.Rmd
Added interactive chart

```{r echo =FALSE, cache=TRUE, include=FALSE, results='asis'}

# Library required packages
library(googleVis)
library(countrycode)
library(repmis)

@@

## Add country codes and place new column at beginning of the data frame
# Create a vector of country codes
D2 <- countrycode(PerceivedOpportunities$Country, "country.name", "iso2c")

@@

# Set columns as numeric
D4[,"2001"] <- as.numeric(D4[,"2001"])
D4[,"2002"] <- as.numeric(D4[,"2002"])
D4[,"2003"] <- as.numeric(D4[,"2003"])
D4[,"2004"] <- as.numeric(D4[,"2004"])
D4[,"2005"] <- as.numeric(D4[,"2005"])
D4[,"2006"] <- as.numeric(D4[,"2006"])
D4[,"2007"] <- as.numeric(D4[,"2007"])
D4[,"2008"] <- as.numeric(D4[,"2008"])
D4[,"2009"] <- as.numeric(D4[,"2009"])
D4[,"2010"] <- as.numeric(D4[,"2010"])
D4[,"2011"] <- as.numeric(D4[,"2011"])
D4[,"2012"] <- as.numeric(D4[,"2012"])
D4[,"2013"] <- as.numeric(D4[,"2013"])

# Generate a new column with mean of all other columns
D4$mean <- rowMeans(subset(D4, select = c("2001", "2002", "2003", "2004", "2005", "2006", "2007", "2008",
                                          "2009", "2010", "2011", "2012", "2013")), na.rm = TRUE)

# Drop year columns, leaving only mean column
D4$'2001' <- NULL
D4$'2002' <- NULL
D4$'2003' <- NULL
D4$'2004' <- NULL
D4$'2005' <- NULL
D4$'2006' <- NULL
D4$'2007' <- NULL
D4$'2008' <- NULL
D4$'2009' <- NULL
D4$'2010' <- NULL
D4$'2011' <- NULL
D4$'2012' <- NULL
D4$'2013' <- NULL

# Create 
D4[, 3] <- round(log(D4[, 3]), digits = 2)
```

### Variation in Perceived Opportunities in OECD
```{r echo =FALSE, cache=TRUE, include=TRUE, results='asis'}
# Plot
Opp_map <- gvisGeoChart(D4, locationvar = 'iso2c',
                      colorvar = 'mean',
                      options = list(
                        colors = "['#fff7bc', '#d95f0e']"
))

print(Opp_map, tag = 'chart')

@@

<br>

<br

### Distribution of Perceived Opportunities in OECD Countries

```{r echo =FALSE, cache=FALSE, include=TRUE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
library(ggvis)

D4 %>% ggvis(~mean, fill := "#2c7fb8") %>% layer_histograms(width = 0.2)

#D4 %>% 
 # ggvis(~mean, fill := "#2c7fb8") %>% 
  #layer_histograms(width =  input_slider(0, 2, step = 0.10, label = "width"),
   #                center = input_slider(0, 2, step = 0.05, label = "center"))

>>>>

```{r echo =FALSE, cache=FALSE, include=TRUE, results='asis', warning=FALSE, error=FALSE, message=FALSE}
library(ggvis)
library("devtools")
library(googleVis)
library(countrycode)
library(repmis)
library(reshape2)
library(RJSONIO)
library(shiny)
library(httpuv)

@@

## Add country codes and place new column at beginning of the data frame
# Create a vector of country codes

D2 <- countrycode(PerceivedOpportunities$Country, "country.name", "iso2c")

@@

# Melt D4 df
D6 <- melt(data = D4,
                  id.vars = c("Country", "iso2c"),
                  measure.vars = c("2001", "2002", "2003", "2004", "2005", "2006",
                                   "2007", "2008", "2009", "2010"))

# Change column titles to  year and PerceivedOpportunities
names(D6) <- gsub("value", "PerceivedOpportunities", names(D6))    
names(D6) <- gsub("variable", "Year", names(D6))

# Set columns as numeric
D6[,"PerceivedOpportunities"] <- as.numeric(D6[,"PerceivedOpportunities"])

# Save cleaned df
D7 <- D6

# Create country vector to subset
myvars2 <- c('US','FR','DE','JP','GB')

# Subset D6
D8 <- subset(D6, iso2c %in% myvars2)

# Create a scatterplot
D8 %>% 
  ggvis(~Year, ~PerceivedOpportunities) %>%
  layer_points(fill = ~factor(Country)) %>%
  group_by(Country)

D8 %>%
  ggvis(~Year, ~PerceivedOpportunities) %>%
  layer_points(fill = ~factor(Country)) %>%
  group_by(Country)

@@

```{r echo =FALSE, cache=FALSE, include=TRUE, results='asis', warning=FALSE, error=FALSE, message=FALSE}

CD <- repmis::source_data("https://raw.githubusercontent.com/SamDund/Assign2Education/master/GEMData/CompleteData.csv", header = TRUE, na.strings = "NA")

# Melt CD df

CD2 <- melt(data = CD,
                  id.vars = c("Country", "Year"),
                  measure.vars = c("WayofTeaching", "PercentFear", "PercentNascent", "PercentPerceived",
                                   "PercentOwner", "PercentIntention", "PercentOpportunities"))

names(CD2) <- gsub("variable", "Survey Question", names(CD2))
names(CD2) <- gsub("value", "Response", names(CD2))

CD3 <- na.omit(CD2)

CD$Year <- as.Date(as.character(CD$Year), format = "%Y")

R <- gvisMotionChart(CD, idvar = "Country", timevar = "Year")

print(R, tag = 'chart')
```
